### 2024-09-24 STA304 Term Paper 1/paper/paper.qmd
Add files via upload

---
title: "Urban Crime Dynamics: Trends in Theft and Assault Over 2014 to 2023"
subtitle: "Analyzing Theft and Assault Trends Across Neighborhoods "
author: 
  - Mingxuan Liu
thanks: "Code and data are available at: LINK."
date: 09-21-2024
date-format: long
abstract: "This paper focuses on the temporal and spatial trends of burglary and assault crime rates in different urban areas from 2014 to 2023. Through analyzing the data Neighbourhood Crime Rates, it is found that there are significant differences in robbery and attack rates in different regions and different time periods. And crime in some areas continues to increase, while in others it fluctuates or decreases. In addition, it is worth noting that there is also a correlation between population size and assault rates. Based on the research results, this paper provides targeted management schemes and resource reallocation schemes for the government and law enforcement agencies to reduce the community crime rate."
format: pdf
number-sections: true
# The toc parameter used to create a table of contents was obtained from
# Quarto documentation:
# https://quarto.org/docs/reference/formats/pdf.html
bibliography: references.bib
---
```{r}
#| echo: false
#| warning: false
#### Preamble ####

# Purpose: Produces a document titled "Urban Crime Dynamics: Trends in Theft and Assault from 2014 to 2023" in PDF format upon rendering.
# Author: Mingxuan Liu
# Date: 09-21-2024
# Contact: mingxuan.liu@mail.utoronto.ca
# Pre-requisites: Run the files "01-download_data.R" and "02-data_cleaning.R".
```

```{r}
#| echo: false
#| include: false
#| warning: false
#| message: false

#install.packages("opendatatoronto")
#install.packages("tidyverse")
library(opendatatoronto)
library(tidyverse)

# Retrieve a list of all available data packages from the OpenDataToronto portal
packages <- list_packages(500)
# Display the list of available packages
packages
```

# Introduction {#sec-introduction}

Community crime has always been an inevitable challenge in the process of urban development, especially theft and assault. With the acceleration of urbanization, the increase of population density and the rise of resource demand, the complexity of crime patterns has also increased. Understanding how crime in different communities changes over time and space becomes critical to the problem of building safe communities. Research shows that urban growth often leads to a non-linear increase in crime rate. @bettencourt2007growth also mentioned that communities with larger populations usually experience higher crime rates. This paper mainly analyzes the data of theft and assault rates of each community from 2014 to 2023. To explore the differences in size and crime rates in different communities and the accompanying time fluctuations.

This article focuses on two key aspects of crime data. First, by analyzing trends in theft rates between 2014 and 2023, significant differences were found across communities.Through data analysis in this paper and @oliveira2021more argue that some communities experienced high rates of burglary during the decade, while others experienced relatively flat or small fluctuations in crime. In addition, the burglary rate is analyzed using a boxplot to show the distribution of crime rates over time, revealing which areas have consistently high or fluctuated crime rates. The analysis found that the increase in theft rates in some areas from 2019 May have been influenced by different economic and social conditions at the time: By @syamsuddin2021effect, starting in 2019, the global COVID-19 pandemic forced people to work and study from home, and some people lost their source of income.

Second, the relationship between population size and assault rates in 2019 suggests that communities with larger populations generally have higher crime rates. According to the @bettencourt2007growth, this verifies the city size effect theory, that is, the expansion of city size may lead to higher social interaction and crime rate. However, the fact that some areas with small population have higher assault rate also indicates that crime rate is also affected by unexpected factors other than population size. By using a bar chart to compare the attack rates of each community in 2023, it is shown that some high-traffic communities have significantly higher attack rates than others.This confirms the crime opportunity theory from @oliveira2021more, which states that more densely populated areas have more crime opportunities.

Through the analysis of these aspects, the time and space dimension of crime are discussed in detail. Through a comprehensive analysis of crime dynamics from different aspects of the data, the burglary rate can reflect the economic state of the community, while the assault crime is often related to social tensions and community security. This paper aims to explore these two categories of crime in depth, assessing how they are evolving in the context of a growing urban population. Finally, the conclusion of the study is to propose targeted management intervention measures to relevant judicial departments and law enforcement agencies and how to effectively carry out crime prevention, such as resource redistribution.

# Data {#sec-data}

## Overview {#sec-data-overview}

The dataset used in this analysis is Neighbourhood Crime Rates published by Toronto Police Services, which was last updated on Jan 11, 2024. In addition, this dataset can be found in Toronto Open Data [@citeopendatatoronto] and is considered opendata. Also, an opendata search for "Neighbourhood Crime Rates" in Toronto Open Data had only one matching dataset [@citeopendatatoronto].

The crime data in this dataset is broken down by the different neighbourhoods of Toronto into different types of crime such as assault, auto theft, burglary, robbery, theft, homicide, etc. In addition, the crime rate in this data is calculated according to Statistics Canada's standard that the number of crimes per 100,000 population * per year [@citeopendatatoronto].

The variables included in this analysis are "crime type", referring to various forms of crime and violation, which are called THEFTOVER_RATE_year and ASSAULT_RATE_year in the original data. In addition, the "population number" is used as the comparison data, which is called "POPULATION_2023" in the original data.

The R programming language [@citeR] and `tidyverse` [@citetidyverse] were used to simulate and test the data set. Then, use `opendatatoronto`[@citeopendatatoronto] and `tidyverse` [@citetidyverse] to download Neighbourhood Crime Rates data. Finally, `tidyverse`[@citetidyverse] is used to clean up the original data, select the required data information to clean up the data that does not meet the requirements, and test the cleaned data again.

## Results {#sec-data-results}
```{r}
#| echo: false
#| warning: false
# Search for a specific package on OpenDataToronto by keyword ("Neighbourhood Crime Rates")
crime_rates_packages <- search_packages("Neighbourhood Crime Rates")

# Retrieve a list of all resources (datasets) available within the found package
crime_rates_resources <- crime_rates_packages %>%
  list_package_resources()

crime_rates_statistics <- crime_rates_resources[8,] %>%
  get_resource()

crime_rates_data = crime_rates_statistics

```
After loading the dataset using the R programming language [@citeR] and the `opendatatoronto` package [@citeopendatatoronto], the `tidyverse` [@citetidyverse] package was used to generate graphs.

# Graph

## Graph 1
\
```{r}
#| echo: false
#| warning: false
#### First Graph ####

library(ggplot2)
library(reshape2)
# This code is based on sample from chatGPT

# Select the columns related to theft rates (2014-2023)
theft_data <- crime_rates_data[, c("AREA_NAME", "THEFTOVER_RATE_2014", "THEFTOVER_RATE_2015", 
                             "THEFTOVER_RATE_2016", "THEFTOVER_RATE_2017", 
                             "THEFTOVER_RATE_2018", "THEFTOVER_RATE_2019",
                             "THEFTOVER_RATE_2020", "THEFTOVER_RATE_2021", 
                             "THEFTOVER_RATE_2022", "THEFTOVER_RATE_2023")]

theft_data_melted <- melt(theft_data, id.vars = "AREA_NAME", variable.name = "Year", value.name = "TheftRate")

# Clean up the contents of the Year column by removing the prefix 'THEFTOVER_RATE_'
theft_data_melted$Year <- gsub("THEFTOVER_RATE_", "", theft_data_melted$Year)
```
\

```{r}
#| echo: false
#| warning: false
#| label: fig-theft-rate-trend-2014-to-2023
#| fig-cap: "Trends in theft rates by region from 2014 to 2023"

# This code is based on sample from chatGPT

# Plot the trend of theft rates in each region over the years
ggplot(theft_data_melted, aes(x = Year, y = TheftRate, group = AREA_NAME, color = AREA_NAME)) +
  geom_line() +
  labs(title = "Trends in theft rates (2014-2023)",
       x = "Year",
       y = "Theft rate (per 100,000 people)") +
  theme_minimal() +
  theme(legend.position = "none")
```

### Graph 1 Analyse

@fig-theft-rate-trend-2014-to-2023 shows the trend of theft rates by region from 2014 to 2023. Most of the areas show a relatively stable and low crime rate for a long time, which may prove that the area has a relatively perfect social security management methods and a relatively stable life state. In addition, crime rates in some areas are more variable and generally higher than in others. It is worth noting that between 2017 and 2019, most regions showed a trend of increasing theft rates, which reflects changes in social conditions or economic development at the time. Overall, theft rates remained relatively flat in most areas, with only slight fluctuations. In addition, there are significant differences in the theft rate in different regions at the same time, which may be related to different social conditions in different regions, such as law enforcement, economic status, population distribution and other factors.

## Graph 2

```{r}
#| label: fig-Box-plot-of-theft-rates
#| echo: false
#| warning: false
#| fig-cap: "box plot in theft rates by region from 2014 to 2023."

#### Second Graph ####

ggplot(theft_data_melted, aes(x = Year, y = TheftRate)) +
  geom_boxplot(aes(fill = Year)) +
  labs(title = "Box plot of theft rates by year (2014-2023)",
       x = "Year",
       y = "Theft rate (per 100,000 people)") +
  theme_minimal() +
  theme(legend.position = "none")
```

### Graph 2 Analyse

The overall distribution of theft rates and their outliers for each region between 2014 and 2023 can be studied using @fig-Box-plot-of-theft-rates. First, while the median showed a relatively flat change, the median theft rate increased slightly between 2018 and 2023. In 2020 and 2021 in particular, the median appears to have reached a higher position. In addition, outliers (indicated by black dots) show unusually high theft rates across years. It is worth mentioning that more significant outliers have appeared in 2019, and the number of outliers has increased significantly. This indicates that in 2019 there were a large number of areas with much higher than general theft rates, and that this was the case in multiple areas. Secondly, the quartile distance also showed a certain fluctuation in this year. The reasons for this may be related to changes in the socio-economic environment during the year, changes in enforcement policies, or social unrest.

## Graph 3

```{r}
#| label: fig-population-and-assault-rate
#| echo: false
#| warning: false
#| fig-cap: "2023 population and assault rate relations with a scatter diagram"
#### Third Graph ####

ggplot(crime_rates_data, aes(x = POPULATION_2023, y = ASSAULT_2023)) +
  geom_point() +
  labs(title = "2023 Population vs 2023 Assault Rate", x = "Population (2023)", y = "Assault Rate (2023)") +
  theme_minimal()
```

### Graph 3 Analyse

@fig-population-and-assault-rate shows that there is no obvious linear relationship between population and attack rates across regions in 2023. However, it can be found that the attack rate in the more populated areas (close to 30,000 people) seems to be relatively high and has an increasing trend, while the attack rate in the less populated areas is more volatile. And there are several outliers that show very high attack rates in areas with higher populations.

## Graph 4

```{r}
#| label: fig-Bar-chart-2023-theft-rates
#| echo: false
#| warning: false
#| fig-cap: "The 20 areas with the highest theft rates in 2023"
#### fourth Graph ####

top_areas <- crime_rates_data[order(-crime_rates_data$THEFTOVER_RATE_2023), ][1:20, ]

# Reorder regions based on 2019 theft rate and plot the bar chart
ggplot(top_areas, aes(x = reorder(AREA_NAME, THEFTOVER_RATE_2023), y = THEFTOVER_RATE_2023, fill = THEFTOVER_RATE_2023)) +
  geom_bar(stat = "identity", show.legend = FALSE) +  
  coord_flip() + 
  geom_text(aes(label = round(THEFTOVER_RATE_2023, 1)), hjust = -0.2, size = 3.5) +  
  labs(title = "Top 20 Areas theft rates in 2023", x = "Area", y = "Theft rate in 2023") +  
  theme_minimal() + 
  scale_fill_gradient(low = "orange", high = "yellow") +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 10), 
        axis.text.y = element_text(size = 10),  
        plot.title = element_text(hjust = 0.5))  
```

### Graph 4 Analyse

This bar chart (@fig-Bar-chart-2023-theft-rates) shows the 20 areas with the highest theft rates in Toronto in 2023. The chart shows that the Yonge-Bay Corridor has a significantly higher theft rate than all other areas, at 312.8. Several other areas with high theft rates, such as Humber Summit and Yorkdale-Glen Park, also had relatively high theft rates of 255 and 235.5, respectively. This suggests that the area may have different conditions or characteristics than other areas, such as high traffic or rich commercial clusters that attract thieves.

# Discussion

This paper examines community crime dynamics, specifically the patterns of theft and assault across time and region. With the rapid progress of urbanization, the higher crime rate may be related to the increase in population density. This article will discuss the effects of socioeconomic, social unrest, and population on crime rates, based on the analysis of theft and assault rates in each region in previous years.

## First discussion point {#sec-first-point}

First of all, @fig-theft-rate-trend-2014-to-2023 emphasizes the spatial distribution of crime and the importance of analyzing crime in time and space dimensions. The data chart shows that theft rates vary from place to place at different times. Some regions have maintained steady fluctuations, while others have fluctuated more. This is connected with the research of @newton2015crime. They believe that the crime hotspot often changes with time, for example, different time or social and economic events will affect the criminal's motive. Analyzing trends in theft can help develop targeted crime prevention strategies. In addition, we also found that external shocks, such as Covid-19, also have an impact on crime rates. The @fig-Box-plot-of-theft-rates show that outliers have unusually high values in 2019-2020. In particular, the median theft rate in residential areas also increased significantly, possibly due to the socio-economic unrest caused by the pandemic. In 2019, almost most places are in lockdown due to the Covid-19 epidemic. By @syamsuddin2021effect, there is a study in Makassar, Indonesia, also documented a similar trend where burglary rates increased significantly during lockdowns, especially in residential areas where people were forced to stay at home due to social restrictions. This external impact has greatly changed people's way of life. Many people have lost their source of income, and the economic pressure of burglars provides the motive to commit crimes. According to the @syamsuddin2021effect, this significant change in the theft rate verifies the theory of criminal opportunity.

## Second discussion point

Another key point in the discussion is the impact of demographics on theft rates. The @Population-and-attack-rate shows the relationship between theft rates and population in 2023. Although there is no clear linear relationship, it is not difficult to find that communities with larger populations also tend to show higher rates of assault. This is consistent with the emphasis in @bettencourt2007growth: The non-linear relationship between population growth and crime rate indicates that with the expansion of community size, especially the incidence of crimes such as assaults related to social interaction will also increase. However, the data also shows that some areas, despite having smaller populations, also have unusually high attack rates. This could be related to a lack of local law enforcement or social instability. Local police should step up patrols to reduce conflicts. Second, @fig-Bar-chart-2023-theft-rates shows the 20 areas with the highest theft rates in 2023, and it's not hard to find that the spatial distribution of crime shows significant differences across different neighborhoods. The Yonge-Bay Corridor and Yorkdale-Glen Park areas with large population traffic have higher theft rates. By @wang2019spatial Criminal activity is often concentrated in some specific neighborhoods, which is closely related to the socioeconomic status of the community. Here, the view emphasized by @bettencourt2007growth that communities with higher population density usually have higher assault crime rates has also been verified.

## Weaknesses and next steps

In general, through data analysis and data review, we found that external disturbances such as population size, economic status and Covid-19 would have an impact on the community crime rate.But this paper only for 2014 to 2023, the theft rate and 2023 assault rate is analyzed, without fully considering the other types of crime. To pursue these two modes of crime, the following measures should be taken. For areas with high population flow, police patrols should be increased to reduce the occurrence of conflicts. And for some areas with poor economic conditions, more rescue stations can be established, and plenty of food and daily necessities can make those who have no economic sources can survive and avoid theft or robbery. Developing targeted community safety and crime prevention strategies can help keep communities safe.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

## Diagnostics

\newpage

# References

### 2024-09-24 STA304 Term Paper 1/scripts/00-simulate_data.R

@@ -1,0 +1,152 @@
+#### Preamble ####
+# Purpose: Simulate data sets about crime rates in various regions and 
+# test these data to be true and valid
+# Author: Mingxuan Liu
+# Date: 09-21-2024
+# Contact: mingxuan.liu@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: Install tidyverse packages
+# Any other information needed? [...UPDATE THIS...]
+
+
+#### Workspace setup ####
+library(tidyverse)
+
+#### Simulate data ####
+# Set seed for reproducibility
+set.seed(123)
+
+# Define the number of observations (e.g., 100 areas)
+n <- 100
+
+# Simulate AREA_NAME as a categorical variable
+area_names <- paste("Area", 1:n)
+
+# Simulate THEFTOVER_RATE for years 2014-2023 using normal distribution
+theftover_rate_2014 <- rnorm(n, mean = 50, sd = 20)
+theftover_rate_2015 <- rnorm(n, mean = 55, sd = 22)
+theftover_rate_2016 <- rnorm(n, mean = 60, sd = 25)
+theftover_rate_2017 <- rnorm(n, mean = 65, sd = 30)
+theftover_rate_2018 <- rnorm(n, mean = 70, sd = 35)
+theftover_rate_2019 <- rnorm(n, mean = 75, sd = 40)
+theftover_rate_2020 <- rnorm(n, mean = 80, sd = 45)
+theftover_rate_2021 <- rnorm(n, mean = 85, sd = 50)
+theftover_rate_2022 <- rnorm(n, mean = 90, sd = 55)
+theftover_rate_2023 <- rnorm(n, mean = 95, sd = 60)
+
+# Simulate POPULATION_2023 using normal distribution
+population_2023 <- rnorm(n, mean = 20000, sd = 5000)
+
+# Simulate ASSAULT_2023 using Poisson distribution
+assault_rate_2023 <- rpois(n, lambda = 150)
+
+# Combine all the simulated data into a data frame
+simulated_data <- data.frame(
+  AREA_NAME = area_names,
+  THEFTOVER_RATE_2014 = theftover_rate_2014,
+  THEFTOVER_RATE_2015 = theftover_rate_2015,
+  THEFTOVER_RATE_2016 = theftover_rate_2016,
[…]

### 2024-09-24 STA304 Term Paper 1/scripts/01-download_data.R

@@ -1,0 +1,41 @@
+#### Preamble ####
+# Purpose: Downloads and saves the data from opendatatoronto package and 
+# stores the dataset for inclusion in the primary paper.
+# Author: Mingxuan Liu
+# Date: 09-21-2024
+# Contact: mingxuan.liu@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: Install the opendatatoronto and tidyverse packages.
+
+
+#### Workspace setup ####
+library(opendatatoronto)
+library(tidyverse)
+
+packages <- list_packages(500)
+# Display the list of available packages
+packages
+
+
+#### Download data ####
+packages <- list_packages(500)
+# Display the list of available packages
+packages
+
+crime_rates_packages <- search_packages("Neighbourhood Crime Rates")
+crime_rates_packages
+# Retrieve a list of all resources (datasets) available within the found package
+crime_rates_resources <- crime_rates_packages %>%
+  list_package_resources()
+# Display the list of resources available in the "Neighbourhood Crime Rates" package
+crime_rates_resources
+
+# Download the .csv dataset
+crime_rates_statistics <- crime_rates_resources[8,] %>%
+  get_resource()
+
+#### Save data ####
+# change the_raw_data to whatever name you assigned when you downloaded it.
+crime_rates_statistics
+write_csv(crime_rates_statistics,"/Users/liumingxuan/Desktop/crime.csv")
+         

### 2024-09-24 STA304 Term Paper 1/scripts/00-simulate_data.R
Delete STA304 Term Paper 1 directory

@@ -1,152 +1,0 @@
-#### Preamble ####
-# Purpose: Simulate data sets about crime rates in various regions and 
-# test these data to be true and valid
-# Author: Mingxuan Liu
-# Date: 09-21-2024
-# Contact: mingxuan.liu@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: Install tidyverse packages
-# Any other information needed? [...UPDATE THIS...]
-
-
-#### Workspace setup ####
-library(tidyverse)
-
-#### Simulate data ####
-# Set seed for reproducibility
-set.seed(123)
-
-# Define the number of observations (e.g., 100 areas)
-n <- 100
-
-# Simulate AREA_NAME as a categorical variable
-area_names <- paste("Area", 1:n)
-
-# Simulate THEFTOVER_RATE for years 2014-2023 using normal distribution
-theftover_rate_2014 <- rnorm(n, mean = 50, sd = 20)
-theftover_rate_2015 <- rnorm(n, mean = 55, sd = 22)
-theftover_rate_2016 <- rnorm(n, mean = 60, sd = 25)
-theftover_rate_2017 <- rnorm(n, mean = 65, sd = 30)
-theftover_rate_2018 <- rnorm(n, mean = 70, sd = 35)
-theftover_rate_2019 <- rnorm(n, mean = 75, sd = 40)
-theftover_rate_2020 <- rnorm(n, mean = 80, sd = 45)
-theftover_rate_2021 <- rnorm(n, mean = 85, sd = 50)
-theftover_rate_2022 <- rnorm(n, mean = 90, sd = 55)
-theftover_rate_2023 <- rnorm(n, mean = 95, sd = 60)
-
-# Simulate POPULATION_2023 using normal distribution
-population_2023 <- rnorm(n, mean = 20000, sd = 5000)
-
-# Simulate ASSAULT_2023 using Poisson distribution
-assault_rate_2023 <- rpois(n, lambda = 150)
-
-# Combine all the simulated data into a data frame
-simulated_data <- data.frame(
-  AREA_NAME = area_names,
-  THEFTOVER_RATE_2014 = theftover_rate_2014,
-  THEFTOVER_RATE_2015 = theftover_rate_2015,
-  THEFTOVER_RATE_2016 = theftover_rate_2016,
[…]

### 2024-09-24 STA304 Term Paper 1/scripts/03-test_data.R

@@ -1,77 +1,0 @@
-#### Preamble ####
-# Purpose: Test these data to be true and valid
-# Author: Mingxuan Liu
-# Date: 09-21-2024
-# Contact: mingxuan.liu@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: Run the files "01-download_data.R" and "02-data_cleaning.R".
-
-
-#### Workspace setup ####
-library(tidyverse)
-
-#### Test raw data  ####
-# Load the data
-crime_rates_statistics <- read.csv("/Users/liumingxuan/Desktop/crime.csv")
-
-# Select a column (e.g., "AUTOTHEFT_RATE_2015") and check if all values are >= 0
-column_name <- "AUTOTHEFT_RATE_2015"
-if (all(crime_rates_statistics[[column_name]] >= 0, na.rm = TRUE)) {
-  print("All non-missing values are greater than or equal to 0")
-} else {
-  print("Some values are less than 0")
-}
-
-#### Test clean data ####
-# Simulate the dataset as previously defined
-set.seed(123)
-n <- 100
-area_names <- paste("Area", 1:n)
-theftover_rate_2014 <- rnorm(n, mean = 50, sd = 20)
-theftover_rate_2015 <- rnorm(n, mean = 55, sd = 22)
-theftover_rate_2016 <- rnorm(n, mean = 60, sd = 25)
-theftover_rate_2017 <- rnorm(n, mean = 65, sd = 30)
-theftover_rate_2018 <- rnorm(n, mean = 70, sd = 35)
-theftover_rate_2019 <- rnorm(n, mean = 75, sd = 40)
-theftover_rate_2020 <- rnorm(n, mean = 80, sd = 45)
-theftover_rate_2021 <- rnorm(n, mean = 85, sd = 50)
-theftover_rate_2022 <- rnorm(n, mean = 90, sd = 55)
-theftover_rate_2023 <- rnorm(n, mean = 95, sd = 60)
-population_2023 <- rnorm(n, mean = 20000, sd = 5000)
-assault_rate_2023 <- rpois(n, lambda = 150)
-
-# Create a data frame
-simulated_data <- data.frame(
-  AREA_NAME = area_names,
-  THEFTOVER_RATE_2014 = theftover_rate_2014,
-  THEFTOVER_RATE_2015 = theftover_rate_2015,
-  THEFTOVER_RATE_2016 = theftover_rate_2016,
[…]

### 2024-09-24 STA304 Term Paper 1/paper/paper.qmd
Add files via upload

@@
   - Mingxuan Liu
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: https://github.com/MingxuanLiu506/Crime_Rate.git"
 date: 09-21-2024

### 2024-09-24 STA304 Term Paper 1/scripts/02-data_cleaning.R

@@ -1,0 +1,36 @@
+#### Preamble ####
+# Purpose: Select specific columns from the dataset, which is needed in this 
+# case are related to theft rates
+# Author:  Mingxuan Liu
+# Date: 09-21-2024
+# Contact: mingxuan.liu@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: Run the file "01-download_data.R".
+
+#### Workspace setup ####
+library(tidyverse)
+
+#### Clean data ####
+# Read the original CSV file
+crime_rates_statistics <- read_csv("/Users/liumingxuan/Desktop/crime.csv")
+
+# Select the relevant columns using dplyr's select function from tidyverse
+selected_columns <- crime_rates_statistics%>%
+  select(AREA_NAME, 
+         THEFTOVER_RATE_2014, 
+         THEFTOVER_RATE_2015, 
+         THEFTOVER_RATE_2016, 
+         THEFTOVER_RATE_2017, 
+         THEFTOVER_RATE_2018, 
+         THEFTOVER_RATE_2019, 
+         THEFTOVER_RATE_2020, 
+         THEFTOVER_RATE_2021, 
+         THEFTOVER_RATE_2022, 
+         THEFTOVER_RATE_2023, 
+         POPULATION_2023, 
+         ASSAULT_RATE_2023)
+
+#### Save data ####
+write_csv(selected_columns, "/Users/liumingxuan/Desktop/STA304 Term Paper 1/clean_data.csv")
+
+

### 2024-09-24 STA304 Term Paper 1/scripts/03-test_data.R

@@ -1,0 +1,77 @@
+#### Preamble ####
+# Purpose: Test these data to be true and valid
+# Author: Mingxuan Liu
+# Date: 09-21-2024
+# Contact: mingxuan.liu@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: Run the files "01-download_data.R" and "02-data_cleaning.R".
+
+
+#### Workspace setup ####
+library(tidyverse)
+
+#### Test raw data  ####
+# Load the data
+crime_rates_statistics <- read.csv("/Users/liumingxuan/Desktop/crime.csv")
+
+# Select a column (e.g., "AUTOTHEFT_RATE_2015") and check if all values are >= 0
+column_name <- "AUTOTHEFT_RATE_2015"
+if (all(crime_rates_statistics[[column_name]] >= 0, na.rm = TRUE)) {
+  print("All non-missing values are greater than or equal to 0")
+} else {
+  print("Some values are less than 0")
+}
+
+#### Test clean data ####
+# Simulate the dataset as previously defined
+set.seed(123)
+n <- 100
+area_names <- paste("Area", 1:n)
+theftover_rate_2014 <- rnorm(n, mean = 50, sd = 20)
+theftover_rate_2015 <- rnorm(n, mean = 55, sd = 22)
+theftover_rate_2016 <- rnorm(n, mean = 60, sd = 25)
+theftover_rate_2017 <- rnorm(n, mean = 65, sd = 30)
+theftover_rate_2018 <- rnorm(n, mean = 70, sd = 35)
+theftover_rate_2019 <- rnorm(n, mean = 75, sd = 40)
+theftover_rate_2020 <- rnorm(n, mean = 80, sd = 45)
+theftover_rate_2021 <- rnorm(n, mean = 85, sd = 50)
+theftover_rate_2022 <- rnorm(n, mean = 90, sd = 55)
+theftover_rate_2023 <- rnorm(n, mean = 95, sd = 60)
+population_2023 <- rnorm(n, mean = 20000, sd = 5000)
+assault_rate_2023 <- rpois(n, lambda = 150)
+
+# Create a data frame
+simulated_data <- data.frame(
+  AREA_NAME = area_names,
+  THEFTOVER_RATE_2014 = theftover_rate_2014,
+  THEFTOVER_RATE_2015 = theftover_rate_2015,
+  THEFTOVER_RATE_2016 = theftover_rate_2016,
[…]

### 2024-09-24 STA304 Term Paper 1/scripts/01-download_data.R
Delete STA304 Term Paper 1 directory

@@ -1,41 +1,0 @@
-#### Preamble ####
-# Purpose: Downloads and saves the data from opendatatoronto package and 
-# stores the dataset for inclusion in the primary paper.
-# Author: Mingxuan Liu
-# Date: 09-21-2024
-# Contact: mingxuan.liu@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: Install the opendatatoronto and tidyverse packages.
-
-
-#### Workspace setup ####
-library(opendatatoronto)
-library(tidyverse)
-
-packages <- list_packages(500)
-# Display the list of available packages
-packages
-
-
-#### Download data ####
-packages <- list_packages(500)
-# Display the list of available packages
-packages
-
-crime_rates_packages <- search_packages("Neighbourhood Crime Rates")
-crime_rates_packages
-# Retrieve a list of all resources (datasets) available within the found package
-crime_rates_resources <- crime_rates_packages %>%
-  list_package_resources()
-# Display the list of resources available in the "Neighbourhood Crime Rates" package
-crime_rates_resources
-
-# Download the .csv dataset
-crime_rates_statistics <- crime_rates_resources[8,] %>%
-  get_resource()
-
-#### Save data ####
-# change the_raw_data to whatever name you assigned when you downloaded it.
-crime_rates_statistics
-write_csv(crime_rates_statistics,"/Users/liumingxuan/Desktop/crime.csv")
-         

### 2024-09-24 STA304 Term Paper 1/scripts/02-data_cleaning.R

@@ -1,36 +1,0 @@
-#### Preamble ####
-# Purpose: Select specific columns from the dataset, which is needed in this 
-# case are related to theft rates
-# Author:  Mingxuan Liu
-# Date: 09-21-2024
-# Contact: mingxuan.liu@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: Run the file "01-download_data.R".
-
-#### Workspace setup ####
-library(tidyverse)
-
-#### Clean data ####
-# Read the original CSV file
-crime_rates_statistics <- read_csv("/Users/liumingxuan/Desktop/crime.csv")
-
-# Select the relevant columns using dplyr's select function from tidyverse
-selected_columns <- crime_rates_statistics%>%
-  select(AREA_NAME, 
-         THEFTOVER_RATE_2014, 
-         THEFTOVER_RATE_2015, 
-         THEFTOVER_RATE_2016, 
-         THEFTOVER_RATE_2017, 
-         THEFTOVER_RATE_2018, 
-         THEFTOVER_RATE_2019, 
-         THEFTOVER_RATE_2020, 
-         THEFTOVER_RATE_2021, 
-         THEFTOVER_RATE_2022, 
-         THEFTOVER_RATE_2023, 
-         POPULATION_2023, 
-         ASSAULT_RATE_2023)
-
-#### Save data ####
-write_csv(selected_columns, "/Users/liumingxuan/Desktop/STA304 Term Paper 1/clean_data.csv")
-
-

### 2024-09-26 scripts/00-simulate_data.R
download raw_data.csv fiel into fiels named data

@@ -8,9 +8,10 @@
 # Pre-requisites: Install tidyverse packages
 # Any other information needed? [...UPDATE THIS...]
 
-
 #### Workspace setup ####
 library(tidyverse)
+
+create_github_token()
 
 #### Simulate data ####
 # Set seed for reproducibility

### 2024-09-26 scripts/01-download_data.R

@@ -37,5 +37,5 @@ crime_rates_statistics <- crime_rates_resources[8,] %>%
 #### Save data ####
 # change the_raw_data to whatever name you assigned when you downloaded it.
 crime_rates_statistics
-write_csv(crime_rates_statistics,"/Users/liumingxuan/Desktop/crime.csv")
+write_csv(crime_rates_statistics,"data/raw_data.csv")
          

### 2024-09-26 scripts/01-download_data.R
change the name csv file's name and save the clean data into clean_data file

@@ -37,5 +37,5 @@ crime_rates_statistics <- crime_rates_resources[8,] %>%
 #### Save data ####
 # change the_raw_data to whatever name you assigned when you downloaded it.
 crime_rates_statistics
-write_csv(crime_rates_statistics,"data/raw_data.csv")
+write_csv(crime_rates_statistics,"data/raw_data/raw_data.csv")
          

### 2024-09-26 scripts/02-data_cleaning.R

@@ -12,7 +12,7 @@ library(tidyverse)
 
 #### Clean data ####
 # Read the original CSV file
-crime_rates_statistics <- read_csv("/Users/liumingxuan/Desktop/crime.csv")
+crime_rates_statistics <- read_csv("data/raw_data/raw_data.csv")
 
 # Select the relevant columns using dplyr's select function from tidyverse
 selected_columns <- crime_rates_statistics%>%
@@ -31,6 +31,6 @@ selected_columns <- crime_rates_statistics%>%
          ASSAULT_RATE_2023)
 
 #### Save data ####
-write_csv(selected_columns, "/Users/liumingxuan/Desktop/STA304 Term Paper 1/clean_data.csv")
+write_csv(selected_columns, "data/clean_data/clean_data.csv")
 
 

### 2024-09-26 scripts/02-data_cleaning.R
Change the read.csv path,and add some description.Also,Add a column which will use in the paper into the clean data

@@ -28,7 +28,8 @@ selected_columns <- crime_rates_statistics%>%
          THEFTOVER_RATE_2022, 
          THEFTOVER_RATE_2023, 
          POPULATION_2023, 
-         ASSAULT_RATE_2023)
+         ASSAULT_RATE_2023,
+         ASSAULT_2023)
 
 #### Save data ####
 write_csv(selected_columns, "data/clean_data/clean_data.csv")

### 2024-09-26 scripts/03-test_data.R

@@ -12,7 +12,7 @@ library(tidyverse)
 
 #### Test raw data  ####
 # Load the data
-crime_rates_statistics <- read.csv("/Users/liumingxuan/Desktop/crime.csv")
+crime_rates_statistics <- read.csv("data/raw_data/raw_data.csv")
 
 # Select a column (e.g., "AUTOTHEFT_RATE_2015") and check if all values are >= 0
 column_name <- "AUTOTHEFT_RATE_2015"
@@ -23,7 +23,9 @@ if (all(crime_rates_statistics[[column_name]] >= 0, na.rm = TRUE)) {
 }
 
 #### Test clean data ####
+selected_columns <- read_csv("data/clean_data/clean_data.csv")
 # Simulate the dataset as previously defined
+# This code is base on the ChatGPT
 set.seed(123)
 n <- 100
 area_names <- paste("Area", 1:n)
@@ -38,6 +40,7 @@ theftover_rate_2021 <- rnorm(n, mean = 85, sd = 50)
 theftover_rate_2022 <- rnorm(n, mean = 90, sd = 55)
 theftover_rate_2023 <- rnorm(n, mean = 95, sd = 60)
 population_2023 <- rnorm(n, mean = 20000, sd = 5000)
+assault_2023 <- rnorm(n, mean = 95, sd = 60)
 assault_rate_2023 <- rpois(n, lambda = 150)
 
 # Create a data frame
@@ -54,7 +57,8 @@ simulated_data <- data.frame(
   THEFTOVER_RATE_2022 = theftover_rate_2022,
   THEFTOVER_RATE_2023 = theftover_rate_2023,
   POPULATION_2023 = population_2023,
-  ASSAULT_RATE_2023 = assault_rate_2023
+  ASSAULT_RATE_2023 = assault_rate_2023,
+  ASSAULT_2023 = assault_2023
 )
 
 # Define the columns to test

### 2024-09-26 paper/paper.qmd
install the here package,and load the clean data.and add toc: true

--- 2024-09-24 STA304 Term Paper 1/paper/paper.qmd
@@
 format: pdf
+toc: true
 number-sections: true
@@
 
+#loading packages
 #install.packages("opendatatoronto")
 #install.packages("tidyverse")
+install.packages("here")
 library(opendatatoronto)
 library(tidyverse)
-
-# Retrieve a list of all available data packages from the OpenDataToronto portal
-packages <- list_packages(500)
-# Display the list of available packages
-packages
+library(here)
 ```
@@
 #| warning: false
-# Search for a specific package on OpenDataToronto by keyword ("Neighbourhood Crime Rates")
-crime_rates_packages <- search_packages("Neighbourhood Crime Rates")
-
-# Retrieve a list of all resources (datasets) available within the found package
-crime_rates_resources <- crime_rates_packages %>%
-  list_package_resources()
-
-crime_rates_statistics <- crime_rates_resources[8,] %>%
-  get_resource()
-
-crime_rates_data = crime_rates_statistics
+# Load the cleaned data which the required columns have been selected.
+selected_columns <- read.csv(here::here("data/clean_data/clean_data.csv"))
+crime_rates_data = selected_columns
 

### 2024-09-26 paper/paper.qmd
change the graph 1 code and the name of graph 1

@@
 ## Graph 1
-\
+
 ```{r}
+#| label: fig-theft-rate-trend-2014-to-2023
 #| echo: false
 #| warning: false
+#| fig-cap: "Trends in theft Rates in the 15 neighborhoods with the Highest Average theft Rates and the 15 neighborhoods with the Lowest Theft Rates, 2014-2023"
+
 #### First Graph ####
+library(tidyverse)
+# This code is based on sample from ChatGPT
 
-library(ggplot2)
-library(reshape2)
-# This code is based on sample from chatGPT
+# Select relevant columns and gather year and theft rate into long format
+crime_rates_long <- crime_rates_data %>%
+  select(AREA_NAME, starts_with("THEFTOVER_RATE")) %>%
+  gather(key = "Year", value = "TheftRate", -AREA_NAME) %>%
+  mutate(Year = as.integer(sub("THEFTOVER_RATE_", "", Year)))
 
-# Select the columns related to theft rates (2014-2023)
-theft_data <- crime_rates_data[, c("AREA_NAME", "THEFTOVER_RATE_2014", "THEFTOVER_RATE_2015", 
-                             "THEFTOVER_RATE_2016", "THEFTOVER_RATE_2017", 
-                             "THEFTOVER_RATE_2018", "THEFTOVER_RATE_2019",
-                             "THEFTOVER_RATE_2020", "THEFTOVER_RATE_2021", 
-                             "THEFTOVER_RATE_2022", "THEFTOVER_RATE_2023")]
+# Calculate average theft rate across the years for each city
+average_theft_rates <- crime_rates_long %>%
+  group_by(AREA_NAME) %>%
+  summarise(AverageTheftRate = mean(TheftRate, na.rm = TRUE)) %>%
+  ungroup()
 
-theft_data_melted <- melt(theft_data, id.vars = "AREA_NAME", variable.name = "Year", value.name = "TheftRate")
+# Select the top 15 and bottom 15 cities based on average theft rates
+top_cities <- top_n(average_theft_rates, 15, AverageTheftRate)
+bottom_cities <- top_n(average_theft_rates, -15, AverageTheftRate)
 
-# Clean up the contents of the Year column by removing the prefix 'THEFTOVER_RATE_'
-theft_data_melted$Year <- gsub("THEFTOVER_RATE_", "", theft_data_melted$Year)
+# Filter the original long data for these cities
+filtered_data <- crime_rates_long %>%
+  filter(AREA_NAME %in% c(top_cities$AREA_NAME, bottom_cities$AREA_NAME))
+
+# Create the plot
+ggplot(filtered_data, aes(x = Year, y = TheftRate, color = AREA_NAME)) +
+  geom_line() +
+  labs(title = "Trends in Theft Rates (2014-2023)",
+       subtitle = "Top 15 and Bottom 15 Cities by Average Theft Rate",
+       x = "Year",
+       y = "Theft rate per 100,000 people") +
+  theme_minimal() +
+  theme(legend.position = "bottom") +
+  guides(color = guide_legend(nrow = 2, byrow = TRUE))
 ```
-\
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-theft-rate-trend-2014-to-2023
-#| fig-cap: "Trends in theft rates by region from 2014 to 2023"
-
-# This code is based on sample from chatGPT
-
-# Plot the trend of theft rates in each region over the years
-ggplot(theft_data_melted, aes(x = Year, y = TheftRate, group = AREA_NAME, color = AREA_NAME)) +
-  geom_line() +
-  labs(title = "Trends in theft rates (2014-2023)",
-       x = "Year",
-       y = "Theft rate (per 100,000 people)") +
-  theme_minimal() +
-  theme(legend.position = "none")
 ```

### 2024-09-26 paper/paper.qmd
Change the graph 1 analyse and the discussion

@@
 
-@fig-theft-rate-trend-2014-to-2023 shows the trend of theft rates by region from 2014 to 2023.
-Most of the areas show a relatively stable and low crime rate for a long time, which may prove that the area has a relatively perfect social security management methods and a relatively stable life state.
-In addition, crime rates in some areas are more variable and generally higher than in others.
-It is worth noting that between 2017 and 2019, most regions showed a trend of increasing theft rates, which reflects changes in social conditions or economic development at the time.
-Overall, theft rates remained relatively flat in most areas, with only slight fluctuations.
-In addition, there are significant differences in the theft rate in different regions at the same time, which may be related to different social conditions in different regions, such as law enforcement, economic status, population distribution and other factors.
+@fig-theft-rate-trend-2014-to-2023 shows trends in the Top 15 and Bottom 15 Cities by Average Theft Rate from 2014 to 2023.
+Regardless of the theft rate, most areas show relatively stable crime rate in a long period of time, which may prove that this area has relatively perfect social security management mode and relatively stable life state.
+In addition, crime rates vary widely in some areas and are generally higher than in others.
+It is worth noting that between 2019 and 2020, most regions showed a trend of rising theft rates, reflecting changes in social conditions or economic development at the time.
+Overall, theft rates remained relatively flat in most regions, with only slight fluctuations.
+In addition, there are significant differences in the theft rate between different regions during the same period, which may be related to different social conditions in different regions, such as law enforcement efforts, economic conditions, population distribution and other factors.
 
@@
 Another key point in the discussion is the impact of demographics on theft rates.
-The @Population-and-attack-rate shows the relationship between theft rates and population in 2023.
+The @fig-population-and-assault-rate shows the relationship between theft rates and population in 2023.
 Although there is no clear linear relationship, it is not difficult to find that communities with larger populations also tend to show higher rates of assault.

### 2024-09-26 paper/paper.qmd
change the appendix part

@@
 
-# Additional data details
+# Dataset and Graph Sketches {#sec-appendix-sketches}
 
-# Model details {#sec-model-details}
+The dataset used in this paper, and the related sketches generated from the dataset, can be found in the folder named 'sketches' in the folder named 'other' in the GitHub repository
 
-## Posterior predictive check
+# Additional data details {#sec-appendix-cleaning}
 
-## Diagnostics
+The process of data cleansing is to extract the columns required for data analysis in this paper and store them in a new csv file.
 

### 2024-09-27 paper/paper.qmd
Load tidyvers repeatedly and delete the excess
change the introduction and delete some description

@@
 
-Community crime has always been an inevitable challenge in the process of urban development, especially theft and assault.
-With the acceleration of urbanization, the increase of population density and the rise of resource demand, the complexity of crime patterns has also increased.
-Understanding how crime in different communities changes over time and space becomes critical to the problem of building safe communities.
-Research shows that urban growth often leads to a non-linear increase in crime rate.
-@bettencourt2007growth also mentioned that communities with larger populations usually experience higher crime rates.
-This paper mainly analyzes the data of theft and assault rates of each community from 2014 to 2023.
-To explore the differences in size and crime rates in different communities and the accompanying time fluctuations.
+Between 2014 and 2023, as urbanization accelerates, the crime dynamics in Toronto change significantly.
+Crime is concentrated in certain neighborhoods, such as those with poor socioeconomic conditions, where residents tend to face a higher risk of property and violence [@wang2019spatial].
+Since 2020, the Covid-19 outbreak has intensified this trend.
+[@syamsuddin2021effect] noted a spike in thefts in many cities around the world during the pandemic, due to socio-economic instability and reduced social activity caused by lockdowns.
+Toronto's neighbourhoods are no exception, with economic pressures leading to a marked increase in property crime in some neighbourhoods.
+In addition, population growth also increases the chance of crime, and the chance of crime is higher in areas with higher population density and resource shortage [@bettencourt2007growth].
 
-This article focuses on two key aspects of crime data.
-First, by analyzing trends in theft rates between 2014 and 2023, significant differences were found across communities.Through data analysis in this paper and @oliveira2021more argue that some communities experienced high rates of burglary during the decade, while others experienced relatively flat or small fluctuations in crime.
-In addition, the burglary rate is analyzed using a boxplot to show the distribution of crime rates over time, revealing which areas have consistently high or fluctuated crime rates.
-The analysis found that the increase in theft rates in some areas from 2019 May have been influenced by different economic and social conditions at the time: By @syamsuddin2021effect, starting in 2019, the global COVID-19 pandemic forced people to work and study from home, and some people lost their source of income.
+Data on Neighbourhood Crime Rates were obtained, as described in @sec-data-overview.
+This paper mainly analyzes the burglary and assault rates in each community from 2014 to 2023, exploring the differences in community size and crime rates and the accompanying time fluctuations.
+The research focuses on the dynamic change of crime rate in different communities before and after the epidemic (@fig-theft-rate-trend-2014-to-2023 and @fig-Box-plot-of-theft-rates) and the relationship between population density and crime rates in 2023 (@fig-population-and-assault-rate and @fig-Bar-chart-2023-theft-rates).
+By assessing these dynamics, we hope to inform crime prevention and resource allocation in Toronto, particularly in high-risk neighbourhoods where there is a long-term need for more police and social resources.
 
-Second, the relationship between population size and assault rates in 2019 suggests that communities with larger populations generally have higher crime rates.
-According to the @bettencourt2007growth, this verifies the city size effect theory, that is, the expansion of city size may lead to higher social interaction and crime rate.
-However, the fact that some areas with small population have higher assault rate also indicates that crime rate is also affected by unexpected factors other than population size.
-By using a bar chart to compare the attack rates of each community in 2023, it is shown that some high-traffic communities have significantly higher attack rates than others.This confirms the crime opportunity theory from @oliveira2021more, which states that more densely populated areas have more crime opportunities.
-
-Through the analysis of these aspects, the time and space dimension of crime are discussed in detail.
-Through a comprehensive analysis of crime dynamics from different aspects of the data, the burglary rate can reflect the economic state of the community, while the assault crime is often related to social tensions and community security.
-This paper aims to explore these two categories of crime in depth, assessing how they are evolving in the context of a growing urban population.
-Finally, the conclusion of the study is to propose targeted management intervention measures to relevant judicial departments and law enforcement agencies and how to effectively carry out crime prevention, such as resource redistribution.
+The structure of this paper is as follows: {#sec-data-overview} presents the data sources and methodology, {#sec-data-overview} presents the results of the analysis, and {#sec-discussion} discusses the policy implications of the findings, particularly with regard to how to respond to crime hotspots in Toronto.
 
@@
 
-# Graph
-
-## Graph 1
-
 ```{r}
@@
 #### First Graph ####
-library(tidyverse)
 # This code is based on sample from ChatGPT
@@
 
-### Graph 1 Analyse
-
 @fig-theft-rate-trend-2014-to-2023 shows trends in the Top 15 and Bottom 15 Cities by Average Theft Rate from 2014 to 2023.
@@
 In addition, there are significant differences in the theft rate between different regions during the same period, which may be related to different social conditions in different regions, such as law enforcement efforts, economic conditions, population distribution and other factors.
-
-## Graph 2
 
@@
 
-### Graph 2 Analyse
-
 The overall distribution of theft rates and their outliers for each region between 2014 and 2023 can be studied using @fig-Box-plot-of-theft-rates.
@@
 The reasons for this may be related to changes in the socio-economic environment during the year, changes in enforcement policies, or social unrest.
-
-## Graph 3
 
@@
 
-### Graph 3 Analyse
-
 @fig-population-and-assault-rate shows that there is no obvious linear relationship between population and attack rates across regions in 2023.
@@
 And there are several outliers that show very high attack rates in areas with higher populations.
-
-## Graph 4
 
@@
 
-### Graph 4 Analyse
-
 This bar chart (@fig-Bar-chart-2023-theft-rates) shows the 20 areas with the highest theft rates in Toronto in 2023.
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 
@@
 
-## First discussion point {#sec-first-point}
+## First discussion point
 

### 2024-09-27 paper/paper.qmd
change the introduction and the code of graph 2

@@
 
-ggplot(theft_data_melted, aes(x = Year, y = TheftRate)) +
-  geom_boxplot(aes(fill = Year)) +
+# Assuming crime_rates_data is already loaded
+theft_data <- crime_rates_data %>% 
+  select(starts_with("THEFTOVER_RATE"), AREA_NAME) %>%
+  pivot_longer(cols = -AREA_NAME, names_to = "Year", values_to = "TheftRate", 
+               names_prefix = "THEFTOVER_RATE_")
+
+# Generate the box plot with ggplot2
+ggplot(theft_data, aes(x = Year, y = TheftRate, fill = Year)) +
+  geom_boxplot() +
   labs(title = "Box plot of theft rates by year (2014-2023)",
        x = "Year",
-       y = "Theft rate (per 100,000 people)") +
+       y = "Theft rate (Per 100,000 people)") +
   theme_minimal() +

### 2024-09-27 paper/paper.qmd
change the content of Overview

@@
 
-The variables included in this analysis are "crime type", referring to various forms of crime and violation, which are called THEFTOVER_RATE_year and ASSAULT_RATE_year in the original data.
+The variables or measurements included in this analysis are "crime type", referring to various forms of crime and violation, which are called THEFTOVER_RATE_year and ASSAULT_RATE_year in the original data.
 In addition, the "population number" is used as the comparison data, which is called "POPULATION_2023" in the original data.

### 2024-09-27 paper/paper.qmd
change the data analyse

@@
 Between 2014 and 2023, as urbanization accelerates, the crime dynamics in Toronto change significantly.
-Crime is concentrated in certain neighborhoods, such as those with poor socioeconomic conditions, where residents tend to face a higher risk of property and violence [@wang2019spatial].
+Crime is concentrated in specific communities, such as those with poor socio-economic conditions.
+In some marginalized communities in Toronto, due to deteriorating economic conditions and insufficient social resources, the crime rate is always high, and residents in this community are often at higher risk of property and violent crime, such as theft and assault [@wang2019spatial].
+
 Since 2020, the Covid-19 outbreak has intensified this trend.
-[@syamsuddin2021effect] noted a spike in thefts in many cities around the world during the pandemic, due to socio-economic instability and reduced social activity caused by lockdowns.
+Thefts have spiked in many cities around the world during the pandemic due to economic instability worldwide and reduced social interaction due to lockdown policies [@syamsuddin2021effect].
 Toronto's neighbourhoods are no exception, with economic pressures leading to a marked increase in property crime in some neighbourhoods.
-In addition, population growth also increases the chance of crime, and the chance of crime is higher in areas with higher population density and resource shortage [@bettencourt2007growth].
+In addition, population growth is also a factor in the rising crime rate.
+Population growth increases the opportunity for crime, and areas with higher population density and tight resources have more opportunities for crime [@bettencourt2007growth].
+That's because densely populated areas have limited law enforcement resources, and they can't respond to crime suspects everywhere in a short period of time.
 
-Data on Neighbourhood Crime Rates were obtained, as described in @sec-data-overview.
-This paper mainly analyzes the burglary and assault rates in each community from 2014 to 2023, exploring the differences in community size and crime rates and the accompanying time fluctuations.
-The research focuses on the dynamic change of crime rate in different communities before and after the epidemic (@fig-theft-rate-trend-2014-to-2023 and @fig-Box-plot-of-theft-rates) and the relationship between population density and crime rates in 2023 (@fig-population-and-assault-rate and @fig-Bar-chart-2023-theft-rates).
-By assessing these dynamics, we hope to inform crime prevention and resource allocation in Toronto, particularly in high-risk neighbourhoods where there is a long-term need for more police and social resources.
+In order to further explore the spatio-temporal changes of the crime rate in Toronto, this study obtains the crime data of various communities from 2014 to 2023 according to the method described in @sec-data-overview, especially the data of theft and assault rates.
+Through these data, this paper analyzes the change trend of crime rates in different communities during these years.
+The differences between community size and crime rate and the fluctuations in different time periods are discussed.
+In addition, The research focuses on the dynamic change of crime rate in different communities before and after the epidemic (@fig-theft-rate-trend-2014-to-2023 and @fig-Box-plot-of-theft-rates) and the relationship between population density and crime rates in 2023 (@fig-population-and-assault-rate and @fig-Bar-chart-2023-theft-rates).
+By assessing these dynamics, this paper aims to inform law enforcement and city planners in Toronto, particularly with regard to resource allocation and crime prevention in high-risk neighbourhoods.
 
@@
 
-@fig-theft-rate-trend-2014-to-2023 shows trends in the Top 15 and Bottom 15 Cities by Average Theft Rate from 2014 to 2023.
-Regardless of the theft rate, most areas show relatively stable crime rate in a long period of time, which may prove that this area has relatively perfect social security management mode and relatively stable life state.
+The @fig-theft-rate-trend-2014-to-2023 shows trends for the top 15 and bottom 15 cities with average theft rates from 2014 to 2023.
+Regardless of the theft rate, the crime rate in most areas is relatively stable over a long period of time, which may prove that the social security management model in the area is relatively perfect, and the living condition is relatively stable.
 In addition, crime rates vary widely in some areas and are generally higher than in others.
-It is worth noting that between 2019 and 2020, most regions showed a trend of rising theft rates, reflecting changes in social conditions or economic development at the time.
-Overall, theft rates remained relatively flat in most regions, with only slight fluctuations.
-In addition, there are significant differences in the theft rate between different regions during the same period, which may be related to different social conditions in different regions, such as law enforcement efforts, economic conditions, population distribution and other factors.
+Notably, most regions showed a trend of rising theft rates between 2019 and 2020, which is related to the worsening socio-economic conditions caused by the Covid-19 outbreak at the time studied.
+[@syamsuddin2021effect].
+Overall, theft rates remained relatively flat in most areas, with only slight fluctuations.
+In addition, there are clear differences in theft rates between different regions over the same period, which may be related to different social conditions in different regions, such as more opportunities for crime in areas with higher population density and tight resources [@bettencourt2007growth].
+We will discuss the relationship between population and crime rates later on @fig-population-and-assault-rate and @fig-Bar-chart-2023-theft-rates.
 
@@
 Secondly, the quartile distance also showed a certain fluctuation in this year.
-The reasons for this may be related to changes in the socio-economic environment during the year, changes in enforcement policies, or social unrest.
+This is evidence of the abnormal fluctuation in crime rates caused by Covid-19 [@syamsuddin2021effect].
 
@@
 
-@fig-population-and-assault-rate shows that there is no obvious linear relationship between population and attack rates across regions in 2023.
-However, it can be found that the attack rate in the more populated areas (close to 30,000 people) seems to be relatively high and has an increasing trend, while the attack rate in the less populated areas is more volatile.
-And there are several outliers that show very high attack rates in areas with higher populations.
+The @fig-population-and-assault-rate shows that there is no significant linear relationship between population and assault rates by region in 2023.
+However, it can be found that the assault rate in more populated areas (close to 30,000 people) appears to be relatively high and on the rise, while the fluctuation is greater in less populated areas.
+And there are several outliers that show very high rates of assault in more populated areas.
+This is consistent with the point made by Bettencourt et al.
+(2007) that areas with larger populations tend to experience higher crime rates due to increased social interaction and strained resources [@bettencourt2007growth].
 
@@
 
-This bar chart (@fig-Bar-chart-2023-theft-rates) shows the 20 areas with the highest theft rates in Toronto in 2023.
-The chart shows that the Yonge-Bay Corridor has a significantly higher theft rate than all other areas, at 312.8.
-Several other areas with high theft rates, such as Humber Summit and Yorkdale-Glen Park, also had relatively high theft rates of 255 and 235.5, respectively.
-This suggests that the area may have different conditions or characteristics than other areas, such as high traffic or rich commercial clusters that attract thieves.
+This bar chart (@fig-Bar-chart-2023-theft-rates) shows the 20 areas in Toronto with the highest theft rates in 2023.
+The chart shows that the Yonge-Bay Corridor area has a significantly higher theft rate than all other areas, at 312.8.
+Far beyond his several areas with high theft rates, which were 255 and 235.3, 255 and 235.5 respectively.
+Combined with the characteristics of these areas, it is concluded that these areas have a high flow of people or concentrated business districts.
+This phenomenon has also been verified in combination with the urban size effect theory of Bettencourt et al., where people with high traffic or rich commercial clusters attract thieves.
+This suggests that the area may have different conditions or characteristics than other regions, such as high traffic or rich business clusters that attract thieves and become a crime hotspot [@bettencourt2007growth].
 

### 2024-09-27 paper/paper.qmd
Code linting and styling for the R file in the script folder and change the graph 1 code also some description

@@
 #install.packages("tidyverse")
-install.packages("here")
+#install.packages("knitr")
+#install.packages("here")
+#install.packages("kableExtra")
 library(opendatatoronto)
@@
 library(here)
+library(knitr)
+library(kableExtra)
 ```
@@
 
-The structure of this paper is as follows: {#sec-data-overview} presents the data sources and methodology, {#sec-data-overview} presents the results of the analysis, and {#sec-discussion} discusses the policy implications of the findings, particularly with regard to how to respond to crime hotspots in Toronto.
+The structure of this paper is as follows: @sec-data-overview presents the data sources and methodology, @sec-data-overview presents the results of the analysis, and @sec-discussion discusses the policy implications of the findings, particularly with regard to how to respond to crime hotspots in Toronto.
 
@@
 Then, use `opendatatoronto`[@citeopendatatoronto] and `tidyverse` [@citetidyverse] to download Neighbourhood Crime Rates data.
-Finally, `tidyverse`[@citetidyverse] is used to clean up the original data, select the required data information to clean up the data that does not meet the requirements, and test the cleaned data again.
+Finally, `tidyverse`[@citetidyverse] is used to clean up the original data, select the required data information to clean up the data that does not meet the requirements, the sample of clean data can be found in @tbl-cleaned-data .Then test the cleaned data again.
 
@@
 After loading the dataset using the R programming language [@citeR] and the `opendatatoronto` package [@citeopendatatoronto], the `tidyverse` [@citetidyverse] package was used to generate graphs.
+
+```{r}
+#| label: tbl-cleaned-data
+#| tbl-cap: Sample of cleaned lead data 
+#| echo: false
+
+# This code is based on the sample from Alexander (2023).
+data1 <- crime_rates_data[,c(1, 3, 13)]
+
+head(data1, 3) %>%
+  kable(
+    col.names = c("AREA_NAME", "THEFTOVER_RATE_2015", "ASSAULT_RATE_2023"),
+    booktabs = TRUE
+)
+```
 
@@
   theme_minimal() +
-  theme(legend.position = "bottom") +
-  guides(color = guide_legend(nrow = 2, byrow = TRUE))
+  theme(legend.position = "none")
 ```

### 2024-09-27 scripts/00-simulate_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Simulate data sets about crime rates in various regions and 
+# Purpose: Simulate data sets about crime rates in various regions and
 # test these data to be true and valid
 # Author: Mingxuan Liu
 # Date: 09-21-2024
@@ -134,20 +134,21 @@ simulated_data <- data.frame(
 )
 
 # Define the columns to test
-cols_to_test <- c("THEFTOVER_RATE_2014", "THEFTOVER_RATE_2015", "THEFTOVER_RATE_2016", 
-                  "THEFTOVER_RATE_2017", "THEFTOVER_RATE_2018", "THEFTOVER_RATE_2019",
-                  "THEFTOVER_RATE_2020", "THEFTOVER_RATE_2021", "THEFTOVER_RATE_2022", 
-                  "THEFTOVER_RATE_2023", "POPULATION_2023", "ASSAULT_RATE_2023")
+cols_to_test <- c(
+  "THEFTOVER_RATE_2014", "THEFTOVER_RATE_2015", "THEFTOVER_RATE_2016",
+  "THEFTOVER_RATE_2017", "THEFTOVER_RATE_2018", "THEFTOVER_RATE_2019",
+  "THEFTOVER_RATE_2020", "THEFTOVER_RATE_2021", "THEFTOVER_RATE_2022",
+  "THEFTOVER_RATE_2023", "POPULATION_2023", "ASSAULT_RATE_2023"
+)
 
 # Test if values in each column are greater than 0
 for (col in cols_to_test) {
   greater_than_zero <- simulated_data[[col]] > 0
   count_greater_than_zero <- sum(greater_than_zero)
   proportion_greater_than_zero <- mean(greater_than_zero)
-  
+
   print(paste("Column:", col))
   print(paste("Number of values greater than 0:", count_greater_than_zero))
   print(paste("Proportion of values greater than 0:", proportion_greater_than_zero))
   print("----")
 }
-

### 2024-09-27 scripts/01-download_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from opendatatoronto package and 
+# Purpose: Downloads and saves the data from opendatatoronto package and
 # stores the dataset for inclusion in the primary paper.
 # Author: Mingxuan Liu
 # Date: 09-21-2024
@@ -31,11 +31,10 @@ crime_rates_resources <- crime_rates_packages %>%
 crime_rates_resources
 
 # Download the .csv dataset
-crime_rates_statistics <- crime_rates_resources[8,] %>%
+crime_rates_statistics <- crime_rates_resources[8, ] %>%
   get_resource()
 
 #### Save data ####
 # change the_raw_data to whatever name you assigned when you downloaded it.
 crime_rates_statistics
-write_csv(crime_rates_statistics,"data/raw_data/raw_data.csv")
-         
+write_csv(crime_rates_statistics, "data/raw_data/raw_data.csv")

### 2024-09-27 scripts/02-data_cleaning.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Select specific columns from the dataset, which is needed in this 
+# Purpose: Select specific columns from the dataset, which is needed in this
 # case are related to theft rates
 # Author:  Mingxuan Liu
 # Date: 09-21-2024
@@ -15,23 +15,23 @@ library(tidyverse)
 crime_rates_statistics <- read_csv("data/raw_data/raw_data.csv")
 
 # Select the relevant columns using dplyr's select function from tidyverse
-selected_columns <- crime_rates_statistics%>%
-  select(AREA_NAME, 
-         THEFTOVER_RATE_2014, 
-         THEFTOVER_RATE_2015, 
-         THEFTOVER_RATE_2016, 
-         THEFTOVER_RATE_2017, 
-         THEFTOVER_RATE_2018, 
-         THEFTOVER_RATE_2019, 
-         THEFTOVER_RATE_2020, 
-         THEFTOVER_RATE_2021, 
-         THEFTOVER_RATE_2022, 
-         THEFTOVER_RATE_2023, 
-         POPULATION_2023, 
-         ASSAULT_RATE_2023,
-         ASSAULT_2023)
+selected_columns <- crime_rates_statistics %>%
+  select(
+    AREA_NAME,
+    THEFTOVER_RATE_2014,
+    THEFTOVER_RATE_2015,
+    THEFTOVER_RATE_2016,
+    THEFTOVER_RATE_2017,
+    THEFTOVER_RATE_2018,
+    THEFTOVER_RATE_2019,
+    THEFTOVER_RATE_2020,
+    THEFTOVER_RATE_2021,
+    THEFTOVER_RATE_2022,
+    THEFTOVER_RATE_2023,
+    POPULATION_2023,
+    ASSAULT_RATE_2023,
+    ASSAULT_2023
+  )
 
 #### Save data ####
 write_csv(selected_columns, "data/clean_data/clean_data.csv")
-
-

### 2024-09-27 scripts/03-test_data.R

@@ -62,20 +62,21 @@ simulated_data <- data.frame(
 )
 
 # Define the columns to test
-cols_to_test <- c("THEFTOVER_RATE_2014", "THEFTOVER_RATE_2015", "THEFTOVER_RATE_2016", 
-                  "THEFTOVER_RATE_2017", "THEFTOVER_RATE_2018", "THEFTOVER_RATE_2019",
-                  "THEFTOVER_RATE_2020", "THEFTOVER_RATE_2021", "THEFTOVER_RATE_2022", 
-                  "THEFTOVER_RATE_2023", "POPULATION_2023", "ASSAULT_RATE_2023")
+cols_to_test <- c(
+  "THEFTOVER_RATE_2014", "THEFTOVER_RATE_2015", "THEFTOVER_RATE_2016",
+  "THEFTOVER_RATE_2017", "THEFTOVER_RATE_2018", "THEFTOVER_RATE_2019",
+  "THEFTOVER_RATE_2020", "THEFTOVER_RATE_2021", "THEFTOVER_RATE_2022",
+  "THEFTOVER_RATE_2023", "POPULATION_2023", "ASSAULT_RATE_2023"
+)
 
 # Test if values in each column are greater than 0
 for (col in cols_to_test) {
   greater_than_zero <- simulated_data[[col]] > 0
   count_greater_than_zero <- sum(greater_than_zero)
   proportion_greater_than_zero <- mean(greater_than_zero)
-  
+
   print(paste("Column:", col))
   print(paste("Number of values greater than 0:", count_greater_than_zero))
   print(paste("Proportion of values greater than 0:", proportion_greater_than_zero))
   print("----")
 }
-

### 2024-09-27 paper/paper.qmd
change the introduction and abstract part in paper. and add some other information in each scripts.

@@
 date-format: long
-abstract: "This paper focuses on the temporal and spatial trends of burglary and assault crime rates in different urban areas from 2014 to 2023.
+abstract: "This paper focuses on the temporal and spatial trends of burglary and assault crime rates in different neighborhood in Toronto from 2014 to 2023.
 Through analyzing the data Neighbourhood Crime Rates, it is found that there are significant differences in robbery and attack rates in different regions and different time periods.
@@
 In addition, it is worth noting that there is also a correlation between population size and assault rates.
-Based on the research results, this paper provides targeted management schemes and resource reallocation schemes for the government and law enforcement agencies to reduce the community crime rate."
+These findings provide valuable insights for local governments and law enforcement agencies to implement targeted crime prevention strategies, as well as serve as reference examples when similar situations occur in other areas."
 format: pdf
@@
 Thefts have spiked in many cities around the world during the pandemic due to economic instability worldwide and reduced social interaction due to lockdown policies [@syamsuddin2021effect].
-Toronto's neighbourhoods are no exception, with economic pressures leading to a marked increase in property crime in some neighbourhoods.
-In addition, population growth is also a factor in the rising crime rate.
+Toronto's neighbourhoods are no exception, with economic pressures leading to a marked increase in property crime in some neighbourhoods, while others show varying fluctuations in trends.
+In addition, population growth is also a factor in the rising crime rate, which continues to rise in some neighborhoods.
 Population growth increases the opportunity for crime, and areas with higher population density and tight resources have more opportunities for crime [@bettencourt2007growth].
@@
 
-In order to further explore the spatio-temporal changes of the crime rate in Toronto, this study obtains the crime data of various communities from 2014 to 2023 according to the method described in @sec-data-overview, especially the data of theft and assault rates.
+Although there have been studies showing the relationship between crime and economic conditions and population growth, there is still a lack of in-depth research on the dynamics of crime in different communities, especially the dynamic relationship between population density, Covid-19 and crime rates.
+This study will fill this gap through data analysis.
+This study obtains the crime data of various communities from 2014 to 2023 according to the method described in @sec-data-overview, especially the data of theft and assault rates.
 Through these data, this paper analyzes the change trend of crime rates in different communities during these years.
@@
 In addition, The research focuses on the dynamic change of crime rate in different communities before and after the epidemic (@fig-theft-rate-trend-2014-to-2023 and @fig-Box-plot-of-theft-rates) and the relationship between population density and crime rates in 2023 (@fig-population-and-assault-rate and @fig-Bar-chart-2023-theft-rates).
-By assessing these dynamics, this paper aims to inform law enforcement and city planners in Toronto, particularly with regard to resource allocation and crime prevention in high-risk neighbourhoods.
+By assessing these dynamics, this study not only informs law enforcement and urban planners in Toronto, but also in other cities facing similar crime rate challenges, particularly in terms of resource allocation and crime prevention in high-risk neighborhoods.
 
@@
 
-The variables or measurements included in this analysis are "crime type", referring to various forms of crime and violation, which are called THEFTOVER_RATE_year and ASSAULT_RATE_year in the original data.
+The variables or measurements included in this analysis are "crime type", referring to various forms of crime and violation, which are called "THEFTOVER_RATE_YEAR" and "ASSAULT_RATE_YEAR" in the original data.
 In addition, the "population number" is used as the comparison data, which is called "POPULATION_2023" in the original data.

### 2024-09-27 scripts/00-simulate_data.R

@@ -6,7 +6,7 @@
 # Contact: mingxuan.liu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: Install tidyverse packages
-# Any other information needed? [...UPDATE THIS...]
+# other information: all code is appropriately styled using styler and lintr.
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-09-27 scripts/01-download_data.R

@@ -6,6 +6,7 @@
 # Contact: mingxuan.liu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: Install the opendatatoronto and tidyverse packages.
+# other information: all code is appropriately styled using styler and lintr.
 
 
 #### Workspace setup ####

### 2024-09-27 scripts/02-data_cleaning.R

@@ -1,11 +1,12 @@
 #### Preamble ####
-# Purpose: Select specific columns from the dataset, which is needed in this
+# Purpose: Select specific columns from the dataset, which is needed in this 
 # case are related to theft rates
 # Author:  Mingxuan Liu
 # Date: 09-21-2024
 # Contact: mingxuan.liu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: Run the file "01-download_data.R".
+# other information: all code is appropriately styled using styler and lintr.
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-09-27 scripts/03-test_data.R

@@ -5,6 +5,7 @@
 # Contact: mingxuan.liu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: Run the files "01-download_data.R" and "02-data_cleaning.R".
+# other information: all code is appropriately styled using styler and lintr.
 
 
 #### Workspace setup ####

### 2024-09-27 paper/paper.qmd
add some description

@@
 The differences between community size and crime rate and the fluctuations in different time periods are discussed.
-In addition, The research focuses on the dynamic change of crime rate in different communities before and after the epidemic (@fig-theft-rate-trend-2014-to-2023 and @fig-Box-plot-of-theft-rates) and the relationship between population density and crime rates in 2023 (@fig-population-and-assault-rate and @fig-Bar-chart-2023-theft-rates).
+In addition, The research focuses on the dynamic change of crime rate in different neiborhood before and after the Covid-19 (@fig-theft-rate-trend-2014-to-2023 and @fig-Box-plot-of-theft-rates) and the relationship between population density and crime rates in 2023 (@fig-population-and-assault-rate and @fig-Bar-chart-2023-theft-rates).
 By assessing these dynamics, this study not only informs law enforcement and urban planners in Toronto, but also in other cities facing similar crime rate challenges, particularly in terms of resource allocation and crime prevention in high-risk neighborhoods.
@@
 
+### Sample of part of cleaned data
+
 ```{r}
@@
 ```
+
+### crime rate before and after the Covid-19
 
@@
 
+### relationship between population density and crime rates
+
 ```{r}
@@
 This suggests that the area may have different conditions or characteristics than other regions, such as high traffic or rich business clusters that attract thieves and become a crime hotspot [@bettencourt2007growth].
+
+\newpage
 

### 2024-09-27 paper/paper.qmd
add some reference and change the content in result part in the paper

@@
 #install.packages("here")
-#install.packages("kableExtra")
 library(opendatatoronto)
@@
 library(knitr)
-library(kableExtra)
 ```
@@
 ```
-After loading the dataset using the R programming language [@citeR] and the `opendatatoronto` package [@citeopendatatoronto], the `tidyverse` [@citetidyverse] package was used to generate graphs.
+After loading the dataset using the R programming language [@citeR] to do data analyse with the following package:  `opendatatoronto` [@citeopendatatoronto],  `tidyverse` [@citetidyverse],  `here` [@citehere], `knitr` [@citeknitr].
 

### 2024-09-27 scripts/00-simulate_data.R
change the code in 00-simulate_data and update the llm text

@@ -9,146 +9,42 @@
 # other information: all code is appropriately styled using styler and lintr.
 
 #### Workspace setup ####
+
+#this code base on the sample of ChatGPT
+
 library(tidyverse)
 
 create_github_token()
 
 #### Simulate data ####
-# Set seed for reproducibility
-set.seed(123)
-
-# Define the number of observations (e.g., 100 areas)
-n <- 100
-
-# Simulate AREA_NAME as a categorical variable
-area_names <- paste("Area", 1:n)
-
-# Simulate THEFTOVER_RATE for years 2014-2023 using normal distribution
-theftover_rate_2014 <- rnorm(n, mean = 50, sd = 20)
-theftover_rate_2015 <- rnorm(n, mean = 55, sd = 22)
-theftover_rate_2016 <- rnorm(n, mean = 60, sd = 25)
-theftover_rate_2017 <- rnorm(n, mean = 65, sd = 30)
-theftover_rate_2018 <- rnorm(n, mean = 70, sd = 35)
-theftover_rate_2019 <- rnorm(n, mean = 75, sd = 40)
-theftover_rate_2020 <- rnorm(n, mean = 80, sd = 45)
-theftover_rate_2021 <- rnorm(n, mean = 85, sd = 50)
-theftover_rate_2022 <- rnorm(n, mean = 90, sd = 55)
-theftover_rate_2023 <- rnorm(n, mean = 95, sd = 60)
-
-# Simulate POPULATION_2023 using normal distribution
-population_2023 <- rnorm(n, mean = 20000, sd = 5000)
-
-# Simulate ASSAULT_2023 using Poisson distribution
-assault_rate_2023 <- rpois(n, lambda = 150)
-
-# Combine all the simulated data into a data frame
-simulated_data <- data.frame(
-  AREA_NAME = area_names,
-  THEFTOVER_RATE_2014 = theftover_rate_2014,
-  THEFTOVER_RATE_2015 = theftover_rate_2015,
-  THEFTOVER_RATE_2016 = theftover_rate_2016,
-  THEFTOVER_RATE_2017 = theftover_rate_2017,
-  THEFTOVER_RATE_2018 = theftover_rate_2018,
-  THEFTOVER_RATE_2019 = theftover_rate_2019,
-  THEFTOVER_RATE_2020 = theftover_rate_2020,
[…]

### 2024-09-27 scripts/00-simulate_data.R
change the description in 00-simulate_data

@@ -11,14 +11,11 @@
 #### Workspace setup ####
 
 #this code base on the sample of ChatGPT
-
-library(tidyverse)
-
-create_github_token()
-
-#### Simulate data ####
 # Load necessary library
 library(tidyverse)
+
+
+#### Simulate data ####
 
 # Set the seed for reproducibility
 set.seed(123)

### 2024-09-28 paper/paper.qmd
add some description and correct spelling mistakes in README
correct the spelling mistake

@@
 abstract: "This paper focuses on the temporal and spatial trends of burglary and assault crime rates in different neighborhood in Toronto from 2014 to 2023.
-Through analyzing the data Neighbourhood Crime Rates, it is found that there are significant differences in robbery and attack rates in different regions and different time periods.
+Through analyzing the data Neighbourhood Crime Rates, it is found that there are significant differences in theft and assault rates in different regions and different time periods.
 And crime in some areas continues to increase, while in others it fluctuates or decreases.
@@
 
+# This code is based on sample from ChatGPT
+
 # Assuming crime_rates_data is already loaded
@@
 
+# This code is based on sample from ChatGPT
+
 ggplot(crime_rates_data, aes(x = POPULATION_2023, y = ASSAULT_2023)) +
@@
 #### fourth Graph ####
+
+# This code is based on sample from ChatGPT
 
